---
title: "COVID Paper Data Dump"
author: "Alliance SciComm & Consulting, LLC"
date: "1/25/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rmarkdown)
library(knitr)
source("code/load_data.R")
knitr::opts_chunk$set(message=FALSE,echo = FALSE,fig.height=4,warning = FALSE,fig.align = "left")
```

# HERC Job Ad Data

```{r herc_data}
source("code/herc_analysis/load_herc_data.R")
source("code/herc_analysis/get_ecr_ads.R")
source("code/herc_analysis/get_adjuct_ads.R")

ggplot(ten_track_summary) + 
  geom_line(aes(x = MonthPosted, y = n, group = YearPosted, color = YearPosted))+
  labs(y = "All Tenure Track positions")


ggplot(ecr_summary) + 
  geom_line(aes(x = MonthPosted, y = n, group = YearPosted, color = YearPosted))+
  coord_cartesian(ylim = c(0, 1750))+
  labs(y = "Assistant Professor Tenure Track Positions")

ggplot(adjunct_summary) + 
  geom_line(aes(x = MonthPosted, y = n, group = YearPosted, color = YearPosted))+
  labs(y = "Adjunct Positions")


ggplot(fixed_summary) + 
  geom_line(aes(x = MonthPosted, y = n, group = YearPosted, color = YearPosted))+
  labs(y = "Non-Tenure Track Faculty Positions")

```

# Hiring Survey Results
```{r hiring_survey}
source("code/get_hiring_results.R")
```

`r kable(hiring_summary)`

`r kable(inst_summary)`

# Altering Search Strategy Results
```{r strategy_survey}
source("code/get_search_strategy_results.R")

yes_summary %>% 
  filter(concern != "covid_dep_offer") %>% 
  as_tibble() %>% 
  mutate(extent = factor(extent, extent_factors)) %>% 
  ggplot() +
  geom_col(aes(x = fct_rev(extent), y = n)) +
  facet_wrap(~concern) +
  coord_flip()
```

`r kable(respondent_summary)`

`r kable(no_summary)`

`r kable(offer_summary)`

# Full Survey COVID-19 Questions

```{r covid, include=FALSE, message=FALSE, echo=FALSE}
source("code/load_data.R")
source("code/get_remote_data.R")
source("code/get_offers_data.R")
source("code/get_rescinded_demos.R")
source("code/get_rejected_demos.R")
source("code/get_strategy_data.R")
```


## Numbers

1. How many on-site interviews were moved to remote? Q114
  + Overall
    + `r num_moved` onsite interviews were moved to remote interviews
    + `r percent_moved` % of onsite interviews moved to remote

2. How many offers were rescinded due to COVID-19? Q115 
  + Overall data
    + `r offers_rescinded` offers were rescinded, total
    + `r percent_rescinded`% of offers made were rescinded

3. Did applicants alter their strategy? Q116 + follow up survey
  + Overall
    + `r num_changed` respondents reported changing their research strategy to some extent
    + `r percent_changed`% of respondents reported changing their research strategy
    
4. Did applicants reject offers because of COVID-19? 
  + Overall
    + `r num_covid_rej` offers were rejected for COVID-19-related reasons
    + `r percent_covid_rej` percent of all rejected offers were due to COVID-19-related reasons
    + `r response_summary[[13,2]]` rejected offer(s) because of reduced resources directly related to the economic impact of COVID-19
    + `r response_summary[[10,2]]` rejected offer(s) because of other reasons pertaining to the impact of COVID-19

## Rescinded Offers
    + Gender
    
```{r gender_res}
get_plot_summary(res_demo_data, "gender", "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = gender, y=percent_res))
```
    + Racial Minority
    
```{r racial_res}
res_demo_data %>% 
  mutate(race_ethnicity = fct_lump(race_ethnicity, n=4)) %>% 
  get_plot_summary(., "race_ethnicity", "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = race_ethnicity, y = percent_res))+
  coord_flip()+
  theme(#axis.text.x = element_text(angle = 90),
        legend.position = "none")
```
    + Academic Field
    
```{r academic_res}
get_plot_summary(data = res_demo_data, 
                                   x = "research_category", y = "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = research_category, y = percent_res))+
  coord_flip()+
  theme(legend.position = "none")
```
    + Position (PhD, postdoc, other)
    
```{r position_res}
get_plot_summary(res_demo_data, "position", "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = position, y = percent_res))+
  coord_flip()
```

## Altered Strategy
    + Position
    
```{r}
get_plot_summary(strategy_demo_data, "position", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = position, y=percent_res))+
  coord_flip()+
  labs(y = "Percent Changed Strategy")
```
    + First Generation Undergrad 
    
```{r}
get_plot_summary(strategy_demo_data, "first_gen_undergrad", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = first_gen_undergrad, y=percent_res))+
  coord_flip()+
  labs(y = "Percent Changed Strategy")
```
    + First Generation PhD 
    
```{r}
get_plot_summary(strategy_demo_data, "first_gen_phd", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = first_gen_phd, y=percent_res))+
  coord_flip()+
  labs(y = "Percent Changed Strategy")
```
    + Academic Field 
    
```{r}
get_plot_summary(strategy_demo_data, "research_category", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = research_category, y=percent_res))+
  coord_flip()+
  labs(y = "Percent Changed Strategy")
```

### Presentation preparation
    + App Feedback 
    
```{r}
get_plot_summary(strategy_prep_data, "app_feedback", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = app_feedback, y=percent_res))+
  coord_flip()+
  labs(y = "Percent Changed Strategy")
```
    + Interview Feedback 
    
```{r}
get_plot_summary(strategy_prep_data, "interview_feedback", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = interview_feedback, y=percent_res))+
  coord_flip()+
  labs(y = "Percent Changed Strategy")
```


## Applicant-Rejected Offers
      + Gender

```{r}
get_plot_summary(reject_summary_demo, "gender", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = gender, y=percent_res))+
  labs(y = "Percent of Applicant-Rejected Offers")
```
      + Dependents
      
```{r}
get_plot_summary(reject_summary_demo, "dependents", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = dependents, y=percent_res))+
  coord_flip()+
  labs(y = "Percent of Applicant-Rejected Offers")
```
      + Primary Caregiver
      
```{r}
get_plot_summary(reject_summary_demo, "primary_caregiver", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = primary_caregiver, y=percent_res))+
  coord_flip()+
  labs(y = "Percent of Applicant-Rejected Offers")
```
      + Racial Minority - top 4 percentages
      
```{r}
reject_summary_demo %>% 
  get_plot_summary(., "race_ethnicity", "covid_reject") %>% 
  arrange(desc(percent_res)) %>% 
  head(n = 4) %>% 
    ggplot()+
  geom_col(aes(x = race_ethnicity, y = percent_res))+
  coord_flip()+
  theme(#axis.text.x = element_text(angle = 90),
    legend.position = "none")+
  labs(y = "Percent of Applicant-Rejected Offers")
```
      + Income
      
```{r}
get_plot_summary(reject_summary_demo, "income", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = income, y=percent_res))+
  coord_flip()+
  labs(y = "Percent of Applicant-Rejected Offers")
```
      + Disability Status
      
```{r}
get_plot_summary(reject_summary_demo, "disability_status", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = disability_status, y=percent_res))+
  coord_flip()+
  labs(y = "Percent of Applicant-Rejected Offers")
```
      + Academic Field
      
```{r}
get_plot_summary(reject_summary_demo, "research_category", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = research_category, y=percent_res))+
  coord_flip()+
  labs(y = "Percent of Applicant-Rejected Offers")

get_plot_summary(reject_summary_demo, "biomedical", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = biomedical, y=percent_res))+
  coord_flip()+
  labs(y = "Percent of Applicant-Rejected Offers")
```
      + Position (PhD, postdoc, other)
      
```{r}
get_plot_summary(reject_summary_demo, "position", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = position, y=percent_res))+
  coord_flip()+
  labs(y = "Percent of Applicant-Rejected Offers")
```
