---
title: "COVID-19 Questions"
author: "Ada"
date: "October 30, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(message=FALSE,echo = FALSE,fig.height=4,warning = FALSE,fig.align = "left")
source("code/load_data.R")
source("code/get_remote_data.R")
source("code/get_offers_data.R")
source("code/get_rescinded_demos.R")
source("code/get_rejected_demos.R")
source("code/get_strategy_data.R")
```
1. How many on-site interviews were moved to remote? Q114
  + Overall
    + `r num_moved` onsite interviews were moved to remote interviews
    + `r percent_moved` % of onsite interviews moved to remote
  + ~~Differences in institution type?~~
  + Did this impact offers received?
  + Did this impact the likelihood to reject an offer for any reason?

2. How many offers were rescinded due to covid? Q115 -- See `get_rescinded_demos.R`
  + Overall data
    + `r offers_rescinded` offers were rescinded, total
    + `r percent_rescinded`% of offers made were rescinded
  + ~~Differences in institution type?~~ 
  + Demographic differences?
  
    + Gender
    
```{r gender_res}
get_plot_summary(res_demo_data, "gender", "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = gender, y=percent_res))
```
    + Racial Minority
    
```{r racial_res}
res_demo_data %>% 
  mutate(race_ethnicity = fct_lump(race_ethnicity, n=4)) %>% 
  get_plot_summary(., "race_ethnicity", "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = race_ethnicity, y = percent_res))+
  coord_flip()+
  theme(#axis.text.x = element_text(angle = 90),
        legend.position = "none")
```
    + Academic Field
    
```{r academic_res}
get_plot_summary(data = res_demo_data, 
                                   x = "research_category", y = "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = research_category, y = percent_res))+
  coord_flip()+
  theme(legend.position = "none")
```
    + ~~Geographic location (not sure if can pull this, I think we only had them put who they got offers from)~~
    + Position (PhD, postdoc, other)
    
```{r position_res}
get_plot_summary(res_demo_data, "position", "covid_offers_rescinded") %>% 
  ggplot()+
  geom_col(aes(x = position, y = percent_res))+
  coord_flip()
```
    
3. Did applicants alter their strategy? Q116 + follow up survey -- See `get_strategy_data.R`
  + Overall
    + `r num_changed` respondents reported changing their research strategy to some extent
    + `r percent_changed`% of respondents reported changing their research strategy
  + ~~Differences in institution type?~~
  + Demographic differences?
  
    + Position
    
```{r}
get_plot_summary(strategy_demo_data, "position", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = position, y=percent_res))+
  coord_flip()
```
    + First Generation Undergrad 
    
```{r}
get_plot_summary(strategy_demo_data, "first_gen_undergrad", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = first_gen_undergrad, y=percent_res))+
  coord_flip()
```
    + First Generation PhD 
    
```{r}
get_plot_summary(strategy_demo_data, "first_gen_phd", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = first_gen_phd, y=percent_res))+
  coord_flip()
```
    + Academic Field 
    
```{r}
get_plot_summary(strategy_demo_data, "research_category", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = research_category, y=percent_res))+
  coord_flip()
```
  + Preparation
  
    + App Feedback 
    
```{r}
get_plot_summary(strategy_prep_data, "app_feedback", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = app_feedback, y=percent_res))+
  coord_flip()
```
    + Interview Feedback 
    
```{r}
get_plot_summary(strategy_prep_data, "interview_feedback", "covid_alter") %>% 
  ggplot()+
  geom_col(aes(x = interview_feedback, y=percent_res))+
  coord_flip()
```
    
    
4. Did applicants reject offers because of Covid? -- See `get_rejected_demos.R`
  + Overall
    + `r num_covid_rej` offers were rejected for COVID-19-related reasons
    + `r percent_covid_rej` percent of all rejected offers were due to COVID-19-related reasons
  + ~~Differences in institution type?~~
  + Demographic differences?
      + Gender
      
```{r}
get_plot_summary(reject_summary_demo, "gender", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = gender, y=percent_res))
```
      + Dependents
      
```{r}
get_plot_summary(reject_summary_demo, "dependents", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = dependents, y=percent_res))
```
      + Primary Caregiver
      
```{r}
get_plot_summary(reject_summary_demo, "primary_caregiver", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = primary_caregiver, y=percent_res))+
  coord_flip()
```
      + Racial Minority - top 4 percentages
      
```{r}
reject_summary_demo %>% 
  get_plot_summary(., "race_ethnicity", "covid_reject") %>% 
  arrange(desc(percent_res)) %>% 
  head(n = 4) %>% 
    ggplot()+
  geom_col(aes(x = race_ethnicity, y = percent_res))+
  coord_flip()+
  theme(#axis.text.x = element_text(angle = 90),
    legend.position = "none")
```
      + Income
      
```{r}
get_plot_summary(reject_summary_demo, "income", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = income, y=percent_res))+
  coord_flip()
```
      + Disability Status
      
```{r}
get_plot_summary(reject_summary_demo, "disability_status", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = disability_status, y=percent_res))+
  coord_flip()
```
      + Academic Field
      
```{r}
get_plot_summary(reject_summary_demo, "research_category", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = research_category, y=percent_res))+
  coord_flip()

get_plot_summary(reject_summary_demo, "biomedical", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = biomedical, y=percent_res))+
  coord_flip()
```
      + Position (PhD, postdoc, other)
      
```{r}
get_plot_summary(reject_summary_demo, "position", "covid_reject") %>% 
  ggplot()+
  geom_col(aes(x = position, y=percent_res))+
  coord_flip()
```

5. In response to Q52 (How did you respond to any offers received? Please check all that apply.), if participant checked:
  + I rejected offer(s) because of reduced resources directly related to the economic impact of Covid-19
OR
  + I rejected offer(s) because of other reasons pertaining to the impact of Covid-19
    + Are they more likely to be in a certain demographic group?
    + Are reported combined household incomes (Q21) lower in those selecting these responses than in those who do not?
    + Are they more likely to have children or other dependents in their household (Q18)?
    + Are they more likely to be first-generation college/PhD students (Q15, Q16)?
    + Are they more likely to NOT reside in the US (Q14)?
    + Are they more likely to be female (Q7) or from a certain ethnic group (Q10)?
